\documentclass[11pt,a4paper,unicode]{moderncv}

\moderncvtheme[green]{classic}

\usepackage[utf8]{inputenc}

%\usepackage[scale=0.8]{geometry}
\usepackage[margin=0.5in]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
\recomputelengths % required when changes are made to page layout

% Set hyperlink colors
\definecolor{linkcolour}{rgb}{0.35,0.70,0.30}			% hyperlinks setup
\AfterPreamble{\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}}

% Name & Title
\name{Garrett}{Lahmann}
%\title{Software Developer} % Too specific, could get filtered out.

% Contact info
\address{Issaquah, WA 98027}
\phone[mobile]{360.556.1944} % Change before sending
\email{lahmanng@gmail.com} % Change before sending
\social[github][www.github.com/glahmann]{glahmann}
\social[linkedin][www.linkedin.com/in/garrett-lahmann-3246a8b9]{garrett-lahmann}
%\homepage{lahmann.onl}
%\photo[64pt][0.4pt]{linkedFace.jpg} % Don't use for American applications.

\begin{document}

%\vspace*{-3\baselineskip}   % Control line spacing
\maketitle
\vspace{-3\baselineskip}

\section{Skills}

\cvline{Proficient}{C\#, Python, Spark, Java, Git, SQL, U-SQL}
\cvline{Sufficient}{Azure, AWS, C, Databricks, Django, Docker, Golang, HTML, Javascript, Jenkins, PowerShell}
\cvline{Misc.}{Bash/Zsh, Eclipse, Emacs, Jira, Jupyter, Power BI, Rally, Unix/Linux}

\section{Education}

%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}
\cventry{June 2018}{Bachelor of Science in Computer Science and Systems}{\newline University of Washington}{Tacoma}{\textit{GPA: 3.88}}{}
\cventry{June 2013}{Bachelor of Arts in East Asian Studies and Chinese Language}{\newline Western Washington University}{Bellingham}{}{} % Coursework included a focus on Chinese language acquisition, as well as cultural and political studies of China and Japan.

\section{Honors}

\cventry{March 2017}{3rd place}{T-Mobile Big Data Hackathon}{Bellevue}{}{Team Hikeaway: a hike recommendation app. \textit{Contribution}: Wrote backend code for database interaction and algorithm controlling user/hike difficulty levels.}
\cventry{October 2016}{2nd place}{T-Mobile IoT Hackathon}{Seattle}{}{Team BabyBand: a wearable IoT device to help monitor the well-being of your young child. \textit{Contribution}: worked with team using agile development techniques, implemented sensors using Javascript and Node.js, setup bluetooth on the band for interaction with mobile devices.}
% \cventry{June 2016}{Dean's List}{University of Washington}{Tacoma}{}{}
\cventry{June 2016}{Best User Design}{Vive Jam Educational VR Hackathon}{Seattle}{}{VR Fire Drill: a safety simulation that teaches kids how to react in a realistic classroom fire situation. \textit{Contribution}: implemented audio features using Unity, tested program for bugs and usability.}
\cventry{June 2015}{Best Overall}{CodeDay}{Auburn}{}{TravelTag: a travel journal application to keep track of memorable moments. \textit{Contribution}: built interactive map using HTML and CSS, worked with teammates to set project direction, organized flow of website.}

\section{Projects}

%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}
\cventry{C\#, Python, Spark, SQL, Docker}{Container Memory Allocation Discrepancy Research}{Academic}{}{}{An investigation of container resource utilization trends on a cloud-based container deployment platform. Findings presented at 2018 IEEE Workshop on Containers.}
\cventry{Python, MySQL, Django}{Hikeaway}{Team}{}{}{A hike recommendation app that uses databases and AI to find nearby hikes that match most closely to users' skill levels, built with a robust backend that can be integrated into any kind of application.}
\cventry{Java}{Storefront Bid Estimator}{Personal}{}{}{A tool to keep track of bids and minimize losses with a recursive algorithm that optimizes material usage. Simplifies the process of bidding jobs for commercial glass industry professionals.}
%\cventry{Java}{PowerPaint}{}{}{}{Wrote front and backend for a GUI based paint program that allows users to create and save static drawings.}
\cventry{Java}{Tetris}{Personal}{}{}{A GUI based Tetris game built using model view controller and observer design patterns.}
%\cventry{HTML}{Personal Website}{}{}{}{A website to showcase the projects I complete outside of class.}

\section{Professional Experience}

\cventry{2018--Present}{Software Engineer}{T-Mobile}{Bellevue, WA}{}{Build cloud based analytics solutions using Python, Spark, GoLang, and Docker. Analyze utilization and billing data to make efficiency improvement suggestions to app teams.}
\cventry{2017--2018}{Cloud Development Intern}{T-Mobile}{Bellevue, WA}{}{Automate AWS cost and usage analysis using U-SQL, C\#, and Azure resources. Produce reports in Power BI. Build ARM templates to provision Azure resource groups. Create APIs for easier access to billing data. Architect a data flow pipeline from Docker containers to a SQLServer database using Spark and Azure resources.}
\cventry{2016--2018}{Volunteer Coding Instructor}{Coder Dojo}{Bellevue, WA}{}{Educate youth in fundamental coding logic and object oriented programming best practices using Python, Java, and Scratch.}
\cventry{2015--2017}{Commercial Framer}{Eubanks Glass}{Centralia, WA}{}{Built a Java tool to improve accuracy of bidding process and streamline design of commercial window installations.}

\section{Coursework and Extracurriculars}

\cvline{Classes}{Algorithms, Cloud Development, Data Structures, Discrete Math, Operating Systems, Software Development}
\cvline{Clubs}{HuSCII Coding - Officer 2016-2018}
\cvline{Dean's List}{2016,2017,2018}

\closesection{}                   % Needed to renew commands
\renewcommand{\listitemsymbol}{-} % change the symbol for lists

\end{document}
